### 2010-12-28 Documentation/atropos/atropos.tex
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@723 fd2da0a4-d968-48df-9cb5-d8c496287cbf

We first convert each of the 69 labels within the original evaluation
dataset to an individual image.  The remaining steps,
summarized briefly, are the same for each of the 19 subjects.  We
select one subject as an unlabeled target.  The other 18 datasets are
then mapped (as in the script above) to that subject.  We then deform,
individually, the 69 $\times$ 18 label images to the unlabeled
subject.  The label probability map is gained by averaging the 18
deformed images associated with each label.  We repeat this for each
subject.  The following parameters are the most relevant to this discussion:
{\ttfamily  -i  PriorProbabilityImages[3, label\_prob\%02d.nii.gz , 0.5
  ] -m [0.1,1x1x1] -c [5,0] -p Socrates[1] }.  Results, in terms of
Dice overlap, are shown in figure~\ref{fig:hammers}.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=8in]{Figures/final_results_majority_vote_vs_atropos.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small The figure compares the Dice
overlap results from Atropos versus the raw results from majority
voting for each of 68 neuroanatomical regions and, in addition, the
unlabeled portions of the brain from the Hammers evaluation dataset.
We evaluated Atropos via N-fold cross-validation and employed
PriorProbabilityImages for each class where probabilities are gained
by averaging mapped subject labels. The color coding highlights those
regions that have the highest (yellow) and lowest (pink) improvement.
The significance of the improvement, measured by pairwise T-test, is
also shown as is a trinary coding of that improvement as: $+$
significant improvement, $-$ performance reduction, $\sim$ no change.}
\label{fig:hammers}
\end{center}
\end{figure}

>>>>

We first convert each of the 69 labels within the original evaluation
dataset to an individual image.  The remaining steps,
summarized briefly, are the same for each of the 19 subjects.  We
select one subject as an unlabeled target.  The other 18 datasets are
then mapped (as in the script above) to that subject.  We then deform,
individually, the 69 $\times$ 18 label images to the unlabeled
subject.  The label probability map is gained by averaging the 18
deformed images associated with each label.  We repeat this for each
subject.  The following parameters are the most relevant to this discussion:
{\ttfamily  -i  PriorProbabilityImages[3, label\_prob\%02d.nii.gz,0.5] 
-m [0.1,1x1x1] -c [5,0] -p Socrates[1] }.  Results, in terms of
Dice overlap, are shown in figure~\ref{fig:hammers}.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=8in]{Figures/final_results_majority_vote_vs_atropos.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small The figure compares the Dice
overlap results from Atropos versus the raw results from majority
voting for each of 68 neuroanatomical regions and, in addition, the
unlabeled portions of the brain from the Hammers evaluation dataset.
We evaluated Atropos via N-fold cross-validation and employed
PriorProbabilityImages for each class where probabilities are gained
by averaging mapped subject labels. The color coding highlights those
regions that have the highest (yellow) and lowest (pink) improvement.
The significance of the improvement, measured by pairwise T-test, is
also shown as is a trinary coding of that improvement as: $+$
significant improvement, $-$ performance reduction, $\sim$ no change.}
\label{fig:hammers}
\end{center}
\end{figure}
